\begin{center}
\section*{Acknowledgements}
\end{center}

\thispagestyle{empty}

\indent % Dr. Palmer
My foremost thanks goes to Dr. Todd Palmer.  High praise for his work and methods led me to seek out a position in the Nuclear Engineering department at Oregon State University.  His thoroughness in lecture and the rigor he expected of his students pushed me to higher levels of work and offered the knowledge I needed to do so.  Though my time at Oregon State University coincided with his departure from the department, he put forth substantial effort to assure my opportunity for success in finishing my degree and this thesis.

% Dr. Wollaber
Second in influence to this work is undoubtedly Dr. Allan Wollaber of Los Alamos National Laboratory.  My experience working for him at LANL paved the way for this work as well as future work in my career.  As the foremost expert in maximum principles fo rthe implicit Monte Carlo equations, Dr. Wollaber offered a magnificent opportunity for me to expand the existing work on the subject.  His unique combination of detail-oriented derivation, availability, and trust allowed me to grow into academic research.

% Committee
My graduate advisory committee, TODO names, must be thanked for countless hours of reviewing and editing, providing suggestions big and small as this thesis has come together.  Without the painstaking effort of these great individuals, this document would be a poor shaodw to what it is now. 

% Peers
While their efforts are the hardest to quantify, the assistance of my peers in the OSU NERHP department deserve much of my thanks as well.  In particular, my gratitude goes to Alex Long for two long years of struggling through equations and concepts as I sought to grasp the intricacies of radiation transport.

% Wife, kids
While she undoubtedly deserves first mention, certainly the first individual outside of the field of nuclear engineering I must mention is my wife, Heather.  While my ability to clearly explain my work in lay terms left her with an unclear picture of my efforts at best, her encouragement has been unrelenting as he sought to take care of the needs of our growing family.  From hot dinners to sack lunches, and for every diaper changed and midnight feeding, thank you, and I love you! 

% Parents
The encouragement of my parents has likewise enabled me to arrive where I am today.  I feel that unlike most children, my stage of asking ``why'' has never really ended, and their willingness to answer to the best of their ability caused a nearly unsatiable desire for knowledge, which as pushed me to excel in school and continue pursuing my academic development.  Without their positive influence, I shudder to consider who I would be today.

% Gpa Jensen
Lastly, I offer my gratitude to my late grandpa Dr. Evan Jensen.  While many individuals have contributed to my learning and growth, his efforts and accomplishments in the scientific community set guiding markers for me to follow in footsteps similar to his.  I fondly remember my time with Grandpa Jensen and he continues to be missed.